Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-31 paper/paper-DrexelFormat.tex
small change

\section{Deep Learning}\label{sec:DL}
This section covers basic concepts of deep learning. First, Section \ref{subsec:basicDL} introduces deep learning, and next ,Section \ref{subsec:RNN} deals with recurrent neural networks and Long Short Term Memory networks (LSTMs). Finally, Section \ref{subsec:AE} covers auto-encoders.

@@

Figure \ref{fig:withoutBiasNN} shows same neural network as Figure \ref{fig:detail_NN} with $\vec{X}$ and $\bold{W}$. Notice that the figure does not have an added node anymore.

@@

Assume the activation function for an output layer is a sigmoid function $sigm()$ then the second part is
$$
\frac{\partial o_i}{\partial o'_i}
= \frac{\partial}{\partial o'_i}sigm(o'_i)
= sigm(o'_i)\{1-sigm(o'_i)\}
= o_i(1-o_i)
$$

@@

\subsubsection{Long Short Term Memory (LSTM) networks:}\label{LSTM}
	Basic RNNs are known to have problems modeling long term dependencies. When RNN passes the previous output for the current output, some information in the input might or might be needed for future. RNN does not have an ability to filter unnecessary information or to store necessary information. Long Short Term Memory (LSTM) neural networks are precisely designed to handle these problems.

>>>>

\section{Deep Learning}\label{sec:DL}
This section covers basic concepts of deep learning. First, Section \ref{subsec:basicDL} introduces deep learning, and next Section \ref{subsec:RNN} deals with recurrent neural networks and Long Short Term Memory networks (LSTMs). Finally, Section \ref{subsec:AE} covers auto-encoders.

@@

Figure \ref{fig:withoutBiasNN} shows same neural network as Figure \ref{fig:detail_NN} with $\vec{X}$ and $\bold{W}$. Notice that the figure does not have an {\em add} node anymore.

@@

Assume the activation function for an output layer is a sigmoid function $sigm()$ then the second part is
$$
\frac{\partial o_i}{\partial o'_i}
= \frac{\partial}{\partial o'_i}sigm(o'_i)
= sigm(o'_i)\{1-sigm(o'_i)\}
= o_i(1-o_i)
$$
where
$$\frac{d}{dx} sigm(x) = \frac{d}{dx} \frac{1}{1+e^{-x}} = \frac{e^{-x}}{(1+e^{-x})^2} = \frac{1}{1+e^{-x}}(1-\frac{1}{1+e^{-x}}) = sigm(x)\{1-sigm(x)\}$$

@@

\subsubsection{Long Short Term Memory (LSTM) networks:}\label{LSTM}
	Basic RNNs are known to have problems modeling long term dependencies. When RNN passes the previous output for the current output, some information in the input might or might not be needed for future. RNN does not have an ability to filter unnecessary information or to store necessary information. Long Short Term Memory (LSTM) neural networks are precisely designed to handle these problems.
